Automatic Visual Inference for Linear Regression

### 2022-03-16 Milestone_presentation_1/Milestone_presentation_1/Milestone_presentation_1.Rmd
lack citation

---
title: "Automatic Visual Inference for Linear Regression"
subtitle: ""  
author: 
  - "Weihao (Patrick) Li"
date: '`r format(Sys.Date(), format="%B %d, %Y")`'
output:
  xaringan::moon_reader:
    seal: false
    css: [xaringan-themer.css, mine.css]
    nature:
      beforeInit: "scripts/my_macro.js"
      countIncrementalSlides: false
      slideNumberFormat: "%current%/%total%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
---

@@

@@

.caption[
Fig. 4: _A typical CNN with convolutional layers, pooling layers and fully-connected layers._ 
]

@@

#### Let $K$ be the number of **independent evaluations** of a visual test, $s_i , i = 1, ..., K$ be the **number of selections of the evaluations**, and $X$ be the random variable denoting the number of detections. Then, the $p$-value of the visual test is given as: $$P(X\geq x) = \sum_{j=x}^{K}Pr(j|s_1,...,s_K).$$

@@

#### We collect **400** lineup evaluations made by **20** participants in experiment I and **880** lineup evaluations made by **44** participants in experiment II.

#### In total, **442** unique lineups are evaluated by **64** subjects.

#### The power of each lineup from one to five evaluations is estimated.

@@

#### All **decisions** made by $K\choose{K-j}$ different outcomes of $V_{K-j}$ are fitted by **binomial generalized linear models** with **natural logarithm of effect size** as the regressor.

@@

.caption[
Fig. 10: _Quasibinomial GLM fitted for estimated power for different number of evaluations. The plot on the left is for the cubic model, the plot on the right is for the heteroskedasticity model. Power curves for different number of evaluations are drawn in different colors. The dashed line is the power of the conventional test._ 
]]

@@

.caption[
Fig. 11: _Binomial GLM fitted for rejection for different number of evaluations. The plot on the left is for the cubic model, the plot on the right is for the heteroskedasticity model. Power curves for different number of evaluations are drawn in different colors. The dashed line is the power of the conventional test._ 
]]

@@

#### There is a huge gap between the conventional curves and the visual test curves when the natural logarithm of effect size is around $0$ for cubic model, and $2.5$ for heteroskedasticity model.

@@

#### We propose a prototype **automatic visual inference system** for evaluating lineups of residual plots of classical normal linear regression. It currently only detects nonlinearity and heteroskedasticity.

@@

#### Models are trained on **10000 null plots** and **10000 actual data plots** simulated from the cubic model and heteroskedasticity model. 20% training data is used as validation set.

@@

#### Model training is performed with **Tensorflow** and **Keras**.

@@

.caption[
Fig. 16: _Power of the automatic visual test compared to human visual test. The blue curve is the power of the automatic visual test. The dashed line represents the power of the conventional test. The plot on the left is for cubic model, and the plot on the right is for heteroskedasticity._ 
]]

@@

.caption[
Fig. 17: _Power of the automatic visual test with different number of evaluations. The dashed line represents the power of the conventional test. The plot on the left is for cubic model, and the plot on the right is for heteroskedasticity._ 
]]

@@

@@

@@

Thanks

>>>>

---
title: "Automatic Visual Inference for Linear Regression"
subtitle: ""  
author: 
  - "Weihao (Patrick) Li"
date: '`r format(Sys.Date(), format="%B %d, %Y")`'
output:
  xaringan::moon_reader:
    seal: false
    css: [xaringan-themer.css, mine.css]
    nature:
      countdown: 55000
      beforeInit: "scripts/my_macro.js"
      countIncrementalSlides: false
      slideNumberFormat: "%current%/%total%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
---

@@

.caption[
Fig. 3: _A Roberts loom in a weaving shed in 1835 and a Watt steam engine. (https://en.wikipedia.org/wiki/Industrial_Revolution)_ 
]

@@

.caption[
Fig. 4: _A typical CNN with convolutional layers, pooling layers and fully-connected layers. (https://en.wikipedia.org/wiki/Convolutional_neural_network)_ 
]

@@

#### Let $s_i , i = 1, ..., K$ be the **number of plots selected by each observer**. Then, the $p$-value of the visual test is given as: $$P(X\geq x) = \sum_{j=x}^{K}Pr(j|s_1,...,s_K).$$

@@

.pull-left[
#### Experiment I:
- **400** lineup evaluations
- **20** participants
]

.pull-right[
#### Experiment II:
- **880** lineup evaluations
- **44** participants
]

@@

#### **Decisions** made by $K\choose{K-j}$ different outcomes of $V_{K-j}, j = 1, ..., 4$, are fitted by **binomial generalized linear models**.

@@

.caption[
Fig. 10: _Quasibinomial GLM fitted for estimated power for different number of evaluations. The plot on the left is for the cubic model, the plot on the right is for the heteroskedasticity model. Power curves for different number of evaluations are drawn in different colors. The dashed line is the power of the F-test and BP-test._ 
]]

@@

.caption[
Fig. 11: _Binomial GLM fitted for rejection for different number of evaluations. The plot on the left is for the cubic model, the plot on the right is for the heteroskedasticity model. Power curves for different number of evaluations are drawn in different colors. The dashed line is the power of the F-test and BP-test._ 
]]

@@

#### There is a huge gap between the conventional test curves and the visual test curves when the natural logarithm of effect size is around $0$ for cubic model, and $2.5$ for heteroskedasticity model.

@@

#### We propose a prototype **automatic visual inference system** for evaluating lineups of residual plots of classical normal linear regression. It currently only detects non-linearity and heteroskedasticity.

@@

#### Training: 
- $10000$ null plots and $10000$ actual data plots simulated from the cubic model and the heteroskedasticity model
- $20$% are used as validation set

#### Training: 
- $10000$ null plots and $10000$ actual data plots simulated from the cubic model and the heteroskedasticity model
- $20$% are used as validation set

@@

#### Training: 
- $10000$ null plots and $10000$ actual data plots simulated from the cubic model and the heteroskedasticity model
- $20$% are used as validation set

#### Model is trained with **Tensorflow** and **Keras**.

@@

.caption[
Fig. 16: _Power of the automatic visual test compared to human visual test. The blue curve is the power of the automatic visual test. The dashed line is the power of the F-test and BP-test. The plot on the left is for cubic model, and the plot on the right is for heteroskedasticity model._ 
]]

@@

.caption[
Fig. 17: _Power of the automatic visual test with different number of evaluations. The dashed line is the power of the F-test and BP-test. The plot on the left is for cubic model, and the plot on the right is for heteroskedasticity model._ 
]]

@@

#### 1. Visual test is not better than conventional tests in detecting non-linearity and heteroskedasticity from residual plot of classical linear regression model.

#### 2. The idea of automating visual inference with computer vision models is feasible. Improvement of the automatic system still needs to be made to match the human visual test power, however.

#### 3. Increasing the number of computer vision models in an automatic visual inference system will result in greater statistical power. But the amount of improvement will decrease.

@@

.pull-left[
### General-Purpose Automatic Visual Statistical Inference System

#### Adopt the techniques developed in query by example content-based image retrieval to build automatic general-purpose visual inference system based on image comparison.

#### No assumption about the type of the plot and the data generating process will be made.

.pull-right[
### OAVIS: An online automatic visual inference system

#### Deploy the automatic visual inference as an online aplication

#### Use online machien learning to improve system performance dynamically.
]

@@

class: center, middle

# Thanks!

# References

Buja, A. et al. (2009). “Statistical inference for
exploratory data analysis and model diagnostics”. In:
_Philosophical Transactions of the Royal Society A:
Mathematical, Physical and Engineering Sciences_
367.1906, pp. 4361-4383. DOI:
[10.1098/rsta.2009.0120](https://doi.org/10.1098%2Frsta.2009.0120).
URL:
[https://royalsocietypublishing-org.ezproxy.lib.monash.edu.au/doi/full/10.1098/rsta.2009.0120](https://royalsocietypublishing-org.ezproxy.lib.monash.edu.au/doi/full/10.1098/rsta.2009.0120).

Fukushima, K. et al. (1982). “Neocognitron: A
self-organizing neural network model for a mechanism of
visual pattern recognition”. In: _Competition and
cooperation in neural nets_. Springer, pp. 267-285.

<!-- `r BibOptions(style = "markdown");PrintBibliography(myBib)` -->
